\section*{Budget Justification}
\bheading{Personnel (\$272,418)}
\ssheading{David M. MacAlpine (PI; 5.76 calendar months)} Dr. MacAlpine will direct the entire project including the design, execution, analysis, and interpretation of experiments. He will also travel to meetings to present preliminary findings, consult with collaborators and oversee the preparation of manuscripts for publication.

\ssheading{Heather K. MacAlpine (Research Laboratory Analyst II, 12.0 calendar months)} Mrs. MacAlpine will coordinate research efforts of the laboratory.  She has extensive experience managing large data production projects (modENCODE) and has co-authored 12 publications.  Mrs. MacAlpine will focus on dissecting the mechanisms that limit helicase progression in the absence of DNA replication.  She will also address how yeast cells resolve un-replicated gaps during anaphase.  With more than 20 years of experience in molecular biology and yeast genetics, she is ideally suited for these studies. 

\ssheading{Boning Chen (Research Assistant, 6.0 calendar months)}  Ms. Chen will examine the spatiotemporal dynamics of chromatin assembly behind the DNA replication fork.  Ms. Chen has training in both experimental and computational biology. Note, that due to the vagaries of academic accounting that 6 calendar months for a student is equivalent to 100\%  effort.

\ssheading{Kevin Moyung (Research Assistant, 6.0 calendar months)}  Mr. Moyung is a computational biologist developing approaches to generate regulatory networks from chromatin occupancy profiling of ~200 yeast mutant strains. Mr. Moyung also assists Mrs. MacAlpine in the analysis of genomic datasets. Note, that due to the vagaries of academic accounting that 6 calendar months for a student is equivalent to 100\% effort.

\bheading{Other Expenses (\$70,156 year 1; \$58,156 years 2 -- 5)}
\ssheading{Equipment} In year one we are requesting an additional \$12,000 for a new -80C freezer.  Our current freezer which houses all of our genetic strains and frozen DNA samples is older than many of my students and has been a dying a slow and painful death.

\ssheading{Sequencing} We are requesting \$15,000 for next generation sequencing costs.  All sequencing will be done at the Duke Sequencing \& Genomic Technologies Shared Resource.  We will take advantage of the small size of the yeast and Drosophila genomes by utilizing barcodes to multiplex multiple experiments on each sequencing lane.  

\ssheading{Supplies and Reagents}  We are requesting \$10,000 in supplies and reagents for our molecular biology and genetic experiments.  These include common enzymes for molecular biology, kits for library generation, and yeast media supplies

\ssheading{Travel Costs}  We are requesting \$3000 per year to offset travel costs and registration fees to attend conferences and present our data.

\ssheading{Publication Costs}  We are requesting \$4000 per year for publication costs. 

\ssheading{Tuition Remission}
We are requesting \$13,078 in tuition remission for Boning Chen and Kevin Muyong. Tuition remission costs are calculated using the University's `Average Rate Basis (ARB)' methodology which has been approved by our Federal Cognizant Agency (DHHS). These rates are applied consistently across the University, regardless of funding source, based on a percentage of the student's actual salary. The Graduate School sets the rate and the projected rate for 2022-2023 is 37.4\%. 

\bheading{F\&A Cost}
Current awarded indirect cost rate is 61\%. Tuition Remission is excluded from the direct cost base.


